---
title: "Data processing with R"
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
# Global Setup
knitr::opts_chunk$set(
  echo = FALSE, comment = ""
)
# old.hooks <- fansi::set_knit_hooks(knitr::knit_hooks)
# options(max.print = 500, crayon.enabled = TRUE)

library(tidyverse)
if (!requireNamespace("zip", quietly = TRUE)) install.packages("zip")
if (!requireNamespace("xaringan", quietly = TRUE)) install.packages("xaringan")
```

```{r}
session_list <- tibble(
  n = 1:12,
  Date = c(
    seq(lubridate::ymd("2018-07-18"), lubridate::ymd("2018-07-18") + lubridate::weeks(7), by = "7 day"),
    seq(lubridate::ymd("2018-09-24"), lubridate::ymd("2018-11-10"), by = "14 day")
  ),
  Topic = c(
    "Meet R and RStudio", #1
    "Data Types, Packages, Data Collections, Workspaces and RStudio Projects", #2,
    "Functions, dplyr, Single-table dplyr verbs", #3
    "Importing/Exporting Data, Working with dplyr", #4
    "Tidy Data, Two-table dplyr verbs", #5
    "Tidying data with tidyr, Dates with lubridate", #6
    "Working with strings", #7
    "R in Real Life", #8
    "Working With Files", #9
    rep("", 3)
  ),
  Location = c("MKE-1308", rep("MKE-1022", 11)),
  `Start Time` = c(rep("09:15", 8), rep("1pm", 4)),
  Link = ""
)
session_list[1, "Link"] <- "session_01.html"
session_list[2, "Link"] <- "session_02_answers.html"
session_list[3, "Link"] <- "session_03_answers.html"
session_list[4, "Link"] <- "session_04_answers.html"
session_list[5, "Link"] <- "session_05_answers.html"
session_list[6, "Link"] <- "session_06_answers.html"
session_list[7, "Link"] <- "session_07.html"
session_list[8, "Link"] <- "session_08.html"
session_list[9, "Link"] <- "slides/working-with-files.html"
```

<!-- Emoji: https://afeld.github.io/emoji-css/ -->

## Announcements

<details><summary>Assignment for Wednesday, September 5</summary>

> **Use R for a task in your daily work.** 
For sharing with the group, you can use your laptop or the conference system to present your use case, or if it’s easier you can [send me your files](mailto:Garrick.Aden-Buie@moffitt.org) and I’ll present them from my laptop. 
If you’re attending remotely and would like to share with the group, please let me know.

</details>

<details><summary>Assignment for Wednesday, August 29</summary>

> Review [dplyr]{.pkg} joins and the [homework assignment from Session 6](session_06.html#assignment).
Fill in the missing code and complete the tasks in the [cancer_registry_joins.R](materials/06/cancer_registry_join.R) script.
The scripts use the breast cancer registry data, which you can download from the [Session 4 materials page](session_04_materials.html).
You can refer to the section on [Two-Table dplyr Verbs](session_05_answers.html#two-table_dplyr_verbs) or to the page of [animated joins](https://github.com/gadenbuie/tidy-animated-verbs#readme).

</details>

<details><summary>Assignment for Wednesday, August 22</summary>

> Fill in the missing code and complete the tasks in the 
[cancer_registry_dplyr.R](materials/05/cancer_registry_dplyr_partial.R) script.
The data and original script can be downloaded from the [Session 4 materials page](session_04_materials.html), and the partially complete script is in the [Session 5 materials page](session_05_materials.html).
You can refer to the [dplyr]{.pkg} [cheat sheet](resources.html#cheat_sheets) or the section on [dplyr from Session 3](session_03_answers.html#dplyr_basics).

</details>

<details><summary>Travis Gerke, Thursday, June 28, 2018</summary>

> We are pleased to announce the launch of a training series, “Data Processing with R,” for any of you who may be interested.  Beginning on July 18, there will be 8 weekly sessions held on Wednesday mornings, 9:15-11:15. Four bi-weekly sessions will follow the initial series. The first session is in MKE-1308, and the remaining sessions are in MKE-1022.
>
> The goal of the training series is to develop core proficiencies in the R programming language for data processing tasks that are common to CDS core staff, honest brokers, and other team members who undertake similar data querying and provisioning activities. No prior experience is necessary! Garrick Aden-Buie, an expert R developer in my group, will be leading the sessions (and I may join as a student when my schedule permits, so that I can learn some new tricks too!).
>
> If you would like to attend, plan to bring a laptop, as the sessions will be interactive. We ask that you install R, Rstudio, and the devtools package prior to the first day ([instructions available here](system-requirements.html)). Garrick can describe/answer any questions about that process in the first session; the reason for completing the task in advance is to ensure that no security permissions on your machine block you from getting up and running.
</details>

## Next Session

```{r results='asis'}
next_session <- session_list %>%
  filter(Date > Sys.Date()) %>%
  arrange(Date) %>%
  slice(1) %>%
  mutate(
    Date = strftime(Date, "%A, %B %d, %Y"),
    Link = ifelse(Link != "", glue::glue('<a href="{Link}">Session {n}</a>'), "")
  ) %>% 
  select(-Topic, -n)

knitr::kable(next_session, escape = FALSE)
```

## Previous Sessions

```{r results='asis'}
prev_sessions <- session_list %>%
  filter(Date <= Sys.Date()) %>%
  arrange(desc(Date)) %>%
  mutate(
    Date = strftime(Date, "%B %d"),
    Link = ifelse(Link != "", glue::glue('<a href="{Link}">Session {n}</a>'), "")
  ) %>% 
  select(Date, Topic, Link)

knitr::kable(prev_sessions, escape = FALSE)
```
