---
title: Session 2
date: "July 25, 2018"
output:
  html_document:
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

[materials]: session_01_materials.html
[slides]: slides/session_01_slides.html
[gapminder]: http://www.gapminder.org/data/
[cran]: https://cran.rstudio.com/
[metacran]: https://www.r-pkg.org
[cran-task-view]: https://cran.r-project.org/web/views/

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = "", prompt = FALSE, results = "show")
knitr::opts_hooks$set(echo_if_show_results = function(options) {
  if (options$echo_if_show_results) {
    options$echo <- options$results == "show"
  }
  options
})
set.seed(42)
```

## Links

- [Materials]
- [This page without answers](session_02.html)

```{r child="source/session_02_review.Rmd"}
```

## Overview

1. [Packages](#packages)

1. [Collections](#collections): [vectors](#vectors), [lists](#lists), [data frames](#data_frames_and_tibbles)

1. [Data Types Continued](#data_types_continued)
    - [Special data types](#special_data_types): `NA`, `NULL`
    - [Working with data types](#working_with_data-types): `is`, `as`, `class`

1. [Workspaces & RStudio Projects](#workspaces__rstudio_projects)

1. [More Functions](#functions)

1. [Data Processing with `dplyr`](#data_processing)

```{r child="source/session_02_course.Rmd"}
```
