---
title: Session 4 — Materials
date: "August 8, 2018"
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis')
make_listing <- function(filename, path_rel, base_url = "https://gerkelab.github.io/core-r-course") {
  cat(glue::glue('\n- [{filename}]({path_rel})\n\n  ```\n  download.file("{file.path(base_url, path_rel)}", "{filename}")\n  ```\n\n'))
}

needs_zip <- function(zipfile, dirpath) {
  zipfile <- here::here(dirpath, "..", zipfile)
  if (!file.exists(zipfile)) return(TRUE)
  zip_modtime <- fs::file_info(zipfile)$modification_time
  files_modtime <- fs::file_info(fs::dir_ls(dirpath)) %>% pull(modification_time) %>% max()
  zip_modtime < files_modtime
}

SESSION <- "05"
ZIPFILE <- glue::glue("core-r_session-{SESSION}_materials.zip")
SESSION_DIR <- here::here("materials", SESSION)
```

Materials for [Session 5](session_05.html).

## Partially completed [dplyr]{.pkg} homework

You can find the [original file](https://gerkelab.github.io/core-r-course/materials/04/cancer_registry_dplyr.R)
and data in the [Session 4 Materials page](session_04_materials.html).

We completed up to **Task 2** in class, please try to finish the rest on your own.
If you get stuck, you can also look at [my completed notes](https://gerkelab.github.io/core-r-course/materials/04/cancer_registry_dplyr.html)
(but try to use this only to get unstuck!).

```{r}
fs::file_info(fs::dir_ls(SESSION_DIR, regexp = "\\.(R|csv|xlsx)")) %>%
  mutate(path_rel = fs::path_rel(path, here::here())) %>% 
  select(path_rel) %>% 
  mutate(filename = basename(path_rel)) %>% 
  purrr::pwalk(make_listing)
```
