---
title: Session 2
date: "July 25, 2018"
output:
  html_document:
    toc: yes
    toc_float: yes
---

[materials]: session_01_materials.html
[slides]: slides/session_01_slides.html
[gapminder]: http://www.gapminder.org/data/

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = "", prompt = FALSE)
set.seed(42)
```

## Links

- [Materials]

## Review

What kind of values are each of the following?

```r
10L
1.2345
"three"
```

What can you tell me about the value that will be returned when I run:

```{r review01, results='hide'}
runif(1, min = -1)
```

<details><summary>Result</summary>
```{r ref.label="review01", echo=FALSE}
```
</details>

Which of these are valid variable names?

```r
min_height
min.height
minHeight
MINHEIGHT
min-height
.min.height
_min_height
0height
min0height
`Minimum Height`
```

<details><summary>Results</summary>

These are all fine:

```r
min_height <- 14
min.height <- 14
minHeight <- 14
MINHEIGHT <- 14

min0height <- 14
`Minimum Height` <- 14
```

This one works, but creates a hidden variable.

```r
.min.height <- 14
```

These don't work and will cause an error.

```r
# Can't start with an `_`
_min_height <- 14

# This is subtraction
min-height <- 14

# Can't start with a number
0height <- 14
```
</details>

What is the value of each variable after each of the following statements?

```{r review03, results="hide"}
todays_temp <- 31.6666
offset <- 32L
coef <- 1.8
intermed_temp <- todays_temp * coef
todays_temp <- intermed_temp + offset
round(todays_temp, 2)
```

<details><summary>Result</summary>
```{r ref.label="review03", echo=FALSE}
```
</details>

## Topics

1. Data types: `is`, `as`, `class`

1. Collections: vectors, lists, data frames

2. Packages

3. Workspaces & RStudio Projects

4. dplyr
