### dplyr

In the last session we talked about 5 important [dplyr]{.pkg} verbs.
What do each of these functions do?

```r
filter()
```

<details><summary>Answer</summary>

- Pick out observations by their values 
</details>

```r
arrange()
```

<details><summary>Answer</summary>

- Reorder the rows
</details>

```r
select()
```

<details><summary>Answer</summary>

- Pick out variables by their names 
</details>

```r
mutate()
```

<details><summary>Answer</summary>

- Create new variables using existing variables
</details>

```r
summarize()
```

<details><summary>Answer</summary>

- Collapse many values into a single summary 
</details>


What are the three "rules" of [dplyr]{.pkg} verbs?

<details><summary>Answer</summary>

1. The first argument is a data frame.

1. Subsequent arguments describe how the verb will transform the data frame, using column names without `"column_name"`

1. The output is a new data frame.
</details>

### Quick Review

Source the [example_single_patient.R](materials/03/example_single_patient.R) file we created in our last session so that the `example` data frame and [dplyr]{.pkg} are loaded.

`example`:

```{r echo=FALSE, results='asis'}
source(here::here("materials/03/example_single_patient.R"))
knitr::kable(example)
```


#### Review Task

Use the pipe operator `%>%` and [dplyr]{.pkg} verbs to complete the following task:

1. Use the `example` dataset

1. Filter out tumors larger than **10**

1. Calculate `follow_up` time as the number of years between diagnosis and the patient's visit

1. Calculate the average follow up time by `site_code`

<details><summary>Answer</summary>

```{r}
example %>% 
  filter(tumor_size <= 10) %>% 
  mutate(follow_up = age_visit - age_dx) %>% 
  group_by(site_code) %>% 
  summarize(avg_follow_up = mean(follow_up))
```

</details>
