## Review

### Data Types

What kind of values are each of the following?

```r
10L
1.2345
"three"
```

### Functions and Arguments

What can you tell me about the value that will be returned when I run:

```{r review01, results='hide'}
runif(1, min = -1)
```

<details><summary>Result</summary>
```{r ref.label="review01", echo=FALSE, results="show"}
```
</details>

### Variable Names

Which of these are valid variable names?

```r
min_height
min.height
minHeight
MINHEIGHT
min-height
.min.height
_min_height
0height
min0height
`Minimum Height`
```

<details><summary>Results</summary>

These are all fine:

```r
min_height <- 14
min.height <- 14
minHeight <- 14
MINHEIGHT <- 14

min0height <- 14
`Minimum Height` <- 14
```

This one works, but creates a hidden variable.

```r
.min.height <- 14
```

These don't work and will cause an error.

```r
# Can't start with an `_`
_min_height <- 14

# This is subtraction
min-height <- 14

# Can't start with a number
0height <- 14
```
</details>

### Variables & Environment

What is the value of each variable after each of the following statements?

```{r review03, results="hide"}
todays_temp <- 31.6666
offset <- 32L
coef <- 1.8
intermed_temp <- todays_temp * coef
todays_temp <- intermed_temp + offset
round(todays_temp, 2)
```

<details><summary>Result</summary>
```{r ref.label="review03", echo=FALSE, results="show"}
```
</details>

### Getting Help

What do the following functions do?
Use `?`, `??` or the [Help]{.rstudio-tab} pane to learn about each function.
Come up with 1-3 examples of each function in action.

```r
identical(___)

tolower(___)

rep(___)

seq(___)
```

<details><summary>`identical`</summary>

> The safe and reliable way to test two objects for being exactly equal. It returns TRUE in this case, FALSE in every other case.

```{r review-identical, results="show"}
identical(1, 1L)

identical(-0, +0, num.eq = FALSE)

identical(1, NULL)
```
</details>

<details><summary>`tolower`</summary>

> Translate characters in character vectors, in particular from upper to lower case or vice versa.

```{r review-tolower, results="show"}
tolower("APPLE")

tolower("Help")

toupper("banana")
```
</details>

<details><summary>`rep`</summary>

> `rep()` replicates the values in `x`.

```{r review-rep, results="show"}
rep(1:4, 2)
rep(1:4, each = 2)       # not the same.
rep(1:4, c(2,2,2,2))     # same as second.
rep(1:4, c(2,1,2,1))
rep(1:4, each = 2, len = 4)    # first 4 only.
rep(1:4, each = 2, len = 10)   # 8 integers plus two recycled 1's.
rep(1:4, each = 2, times = 3)  # length 24, 3 complete replications
```
</details>

<details><summary>`seq`</summary>

> Generate regular sequences. seq is a standard generic with a default method. seq.int is a primitive which can be much faster but has a few restrictions. seq_along and seq_len are very fast primitives for two common cases.

```{r review-seq, results="show"}
seq(1, 9)
seq(0, 1, by = 0.1)
seq(0, 1, length.out = 11)
seq(1, 9, by = 2)     # matches 'end'
seq(1, 9, by = pi)    # stays below 'end'
seq(1, 6, by = 3)
seq(1.575, 5.125, by = 0.05)
seq(17) # same as 1:17, or even better seq_len(17)
```
</details>

### Highlighting New Concepts

These examples gave us a chance to review the things that we talked about during the last session, and they also introduced us to several new concepts that we will cover today.

1. Vectors

1. What are the `...`? (_further arguments passed to or from other methods_)

1. `NULL` and `NA`
